### 2023-08-16 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
small edits

%%%TITLE, AUTHORS AND ABSTRACT%%%
\twocolumn[
  \begin{@twocolumnfalse}
{\includegraphics[height=30pt]{head_foot/SM}\hfill\raisebox{0pt}[0pt][0pt]{\includegraphics[height=55pt]{head_foot/RSC_LOGO_CMYK}}\\[1ex]
\includegraphics[width=18.5cm]{head_foot/header_bar}}\par
\vspace{1em}
\sffamily
\begin{tabular}{m{4.5cm} p{13.5cm} }
%
\includegraphics{head_foot/DOI} & \noindent\LARGE{\textbf{Hydrodynamics of Multicomponent Vesicles Under Strong Confinement}} \\
\vspace{0.3cm} & \vspace{0.3cm} \\
%
 & \noindent\large{Ashley Gannon,\textit{$^{a}$} Y.-N. Young,\textit{$^{b\ddag}$} and Bryan Quaife\textit{${\ast}${$^{a}$}}} \\
% %Author names go here instead of "Full name", etc.
%
\includegraphics{head_foot/dates} & \noindent\normalsize{We numerically
  study the hydrodynamics of multicomponent vesicles in two strongly
  confining geometries. This serves as a simplified model for red blood
  cells undergoing large deformations when passing through extreme
  constrictions. We propose a new bending modulus parameterization that
  is positive for all values of the lipid phase parameter. For a
  multicomponent vesicle passing through a stenosis, we correlate the
  lipid phase coarsening, the lubrication layer properties (size and
  flow profile), the excess pressure, and the tank-treading velocity of
  the membrane. For a multicomponent vesicle passing through a
  contracting channel, we find that the lipid always phase separates so
  that the vesicle is stiffer in the front as it passes through the
  constriction. For both cases of confinement we find that the lipid
  coarsening is arrested under strong confinement, and proceeds with
  high rate upon relief from extreme confinement. The results may be
  useful for efficient sorting lipid domains using microfluidic flows by
  controlled release of vesicles passing through strong confinement.} \\
  %The abstrast goes here instead of the text "The abstract should
  %be..."
%
\end{tabular}
%
 \end{@twocolumnfalse} \vspace{0.6cm}
]
%%%END OF TITLE, AUTHORS AND ABSTRACT%%%

@@

%%%MAIN TEXT%%%%
\section{\label{sec:Introduction}Introduction}
Biological membranes, the basic structural units for compartmentalizing
biological systems, have been observed to contain a vast array of
proteins and different lipid species that phase-separate and form
domains or rafts, resulting in spatial variations in material properties
such as bending stiffness. Synthetic multicomponent vesicles,
self-enclosed lipid bilayer membranes composed of different lipid
species, have been used to study the rich patterns and accompanying
morphologies that emerge from elastic heterogeneity in the membrane. In
a quiescent environment, such elastic heterogeneity gives rise to
wrinkling, budding, adhesion, and fusion of vesicle
membranes~\cite{Lowengrub2009_PRE, Li2012_CommMathSci, Zhao2011_PRE},
closely related to several cellular processes~\cite{Rauch2000_BiophysJ,
Takeda2003_PNAS}.
%In a quiescent environment, such elastic heterogeneity gives rise to
%wrinkling budding~\cite{Lowengrub2009_PRE, Li2012_CommMathSci},
%adhesion and fusion~\cite{Zhao2011_PRE} of vesicle membrane, closely
%related to cellular budding and fission
%processes~\cite{Rauch2000_BiophysJ} as well as in cellular adhesion and
%fusion~\cite{Takeda2003_PNAS}.

@@

Under a linear shear flow, a multicomponent vesicle exhibits more exotic
dynamics in both shape and membrane composition than a single-component
vesicle~\cite{soh-tse-li-voi-low2010, Smith2007_JChemPhys,
Cox2015_Nonlinearity, liu-mar-li-vee-low2017, Tusch2018_PRF,
Gera2018_SoftMatter, ger-sal-spa2022}. For example, multicomponent
vesicles under a background flow often exhibit highly complex
morphologies, leading to vesicle budding. The hydrodynamics of these
multicomponent vesicles include phase treading, tumbling with no
viscosity contrast, swinging, budding, and
fission~\cite{soh-tse-li-voi-low2010, wan-du2008, all-ama2006,
ger-sal-spa2022, lip1992, urs-klu-phi2009}. Through numerical
investigations,~\citet{liu-mar-li-vee-low2017} identified several key
dimensionless numbers, including the reduced area, capillary number, and
the floppy-to-stiff ratio to characterize various dynamics of a
two-dimensional multicomponent vesicle in an unbounded linear shear
flow. In addition to the aforementioned numerical studies, these
dynamics have been observed in experiments~\cite{bag-sun2009,
yan-ima-tan2010, yan-ima-tan2008, dre-jah-bob-spa-gop2021}.

%
%Sohn et al. (2010) studied two-dimensional multicomponent vesicles in a
%background shear flow, along with the evolution of distinct surface
%phases, finding highly complex morphologies and dynamics for highly
%deformed vesicles. Smith & Uspal (2007) showed using dissipative
%particle dynamics simulations that a shear flow can be used to separate
%buds from a multicomponent vesicle. The influence of both bending
%rigidity and spontaneous curvature variation on the equilibrium shape
%of a vesicle has also been investigated (Cox & Lowengrub 2015).
%Subsequent boundary integral simulations by Liu et al. (2017) showed a
%transition from tumbling to tank-treading to ‘phase-treading’ of the
%constituents along the surface upon increasing the shear rate. Analytic
%results have also shown that a variation of bending rigidity along a
%surface can induce migration in tank-treading vesicles (Olla 2011).
%Synthetic systems have also been fruitful for testing theoretical
%predictions. Experiments using a two-phase lipid vesicle in such a flow
%as a simplified model of red blood cell dynamics showed similarly
%complex features (Tusch et al. 2018). Gera & Salac (2018b) then used
%simulations to probe a wide array of morphological changes due to
%spatially varying bending stiffness and line tension between two lipid
%phases. The phase separation process itself is naturally of great
%interest, and experiments have been used to study spinodal
%decomposition and viscous fingering along membrane surfaces (Veatch &
%Keller 2003; Lowengrub, Rätz & Voigt 2009; Marenduzzo & Orlandini 2013;
%Stanich et al. 2013).
%
%
%Groups have also studied the behaviors of a vesicle that is composed of
%different types of lipids and proteins. The presence of different lipid
%species has been used to model different processes including the
%bending stiffness, spontaneous curvature, and adhesion
%potential~\cite{zha-das-du2010, tan-yan-ima2011}. The dynamics of these
%multicomponent vesicles include phase treading, tumbling with no
%viscosity contrast, swinging, budding, and
%fission~\cite{soh-tse-li-voi-low2010, wan-du2008, all-ama2006,
%ger-sal-spa2022, lip1992, urs-klu-phi2009}. In addition to the
%aforementioned numerical studies, these dynamics have been observed in
%experiments~\cite{bag-sun2009, yan-ima-tan2010, yan-ima-tan2008,
%dre-jah-bob-spa-gop2021}.
%

@@

The lipid species $u$ is governed by a fourth-order Cahn-Hilliard
equation that results in the lipids phase separating while conserving
their total mass. To model the variable bending,
\citet{soh-tse-li-voi-low2010} parameterized the bending modulus as
\begin{align}
  \label{eqn:linearBending}
  b(u) = (1-u) + \beta u.
\end{align}
However, since the double-well potential does not have hard walls, the
lipid concentration is not guaranteed to be confined to the interval
$[0,1]$. This is problematic since $b(u) < 0$ if $u > (1 - \beta)^{-1}$,
and such values of $u$ are possible when $\beta \ll 1$, $Ca \gg 1$, or
the vesicle is confined to a narrow region. This behavior is
demonstrated in Figure~\ref{fig:concModels}(a) for a vesicle with a
floppy-to-stiff ratio $\beta = 10^{-1}$. Using the linear bending model
in Equation~\eqref{eqn:linearBending}, the lipid concentration achieves
a maximum value of $u \approx 1.5$ which results in an instability that
is formed by the resulting unphysical negative bending stiffness. To
rectify this issue, we parameterize the bending modulus with the sigmoid
function
\begin{align}
  b(u) = \frac{\beta-1}{2} \tanh\left(3\left(u-\frac{1}{2} 
    \right)\right) + \frac{\beta + 1}{2}.
  \label{eqn:tanhBending}
\end{align}
This parameterization maps the local minimums of the double-well
potential close to $\beta$ and $1$, but more importantly, b(u) remains
bounded in $(\beta,1)$ even when $u \notin [0,1]$
(Figure~\ref{fig:concModels}(b)). This new bending model is validated in
Section~\ref{sec:validation}.
%To demonstrate the necessity of this new bending model, we consider a
%multicomponent vesicle in strong confinement with both bending
%models~\eqref{eqn:linearBending} and~\eqref{eqn:tanhBending}. The
%stiff-to-floppy ratio is $\beta = 10^{-1}$. In the new
%model~\eqref{eqn:tanhBending}, the lipid concentration achieves a
%maximum value of $u \approx 1.002$ which results in a minimum bending
%stiffness of $b(u) \approx \beta$. However, if we use the linear
%bending model~\eqref{eqn:linearBending}, the lipid concentration
%achieves a maximum value of $u \approx 1.52$ which results in an
%unphysical negative bending stiffness of $b(u) \approx -0.5$. The
%corresponding vesicle shape is in Figure~\ref{fig:concModels}(b), and
%the instability caused by the negative bending stiffness is near the
%region with negative curvature.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Validation}
\label{sec:validation}
We validate the new sigmoid bending model in
Equation~\eqref{eqn:tanhBending} by reproducing dynamics reported in the
literature. Figure~\ref{fig:treading} shows a phase treading (top) and a
tank-treading (bottom) multicomponent vesicle in an unconfined linear
shear flow. The simulations align with the results reported
by~\citet{liu-mar-li-vee-low2017} (cf.~Figure 3).
\begin{figure}[h]
  \centering
  \includegraphics[width=0.9\columnwidth]{figures/shearTreading.pdf}
%  \subfigimg[width=\columnwidth, trim ={5.5cm 1.5cm 4cm 0},clip]{(a)}{figures/Fig4a.pdf}
%  \subfigimg[width=\columnwidth, trim ={5.5cm 1.5cm 4cm 0},clip]{(b)}{figures/Fig4b.pdf}
  \caption{\label{fig:treading} \small A multicomponent vesicle in a
  linear shear flow undergoes phase-treading (top) and tank-treading
  (bottom) with the new sigmoid bending model in
  Equation~\eqref{eqn:tanhBending}. The dimensionless times are in the
  title. The red region is stiff and the blue region is floppy. The
  simulations qualitatively agree with the results presented
  in~\citet{liu-mar-li-vee-low2017}.}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\label{sec:LL} Lubrication layers and excess pressure}
The lubrication layer between a vesicle and the solid wall plays a
critical role in the dynamics of a vesicle under strong confinement.
Therefore, throughout Section~\ref{sec:results}, we calculate and
analyze the flow inside the lubrication layers between the vesicle and
the channel walls to elucidate the correlation between hydrodynamics and
membrane dynamics. To define the size of the top lubrication layer (the
size of the bottom lubrication layer is defined similarly), we let
$d(\xx,\Gamma_\mathrm{top})$ be the minimum distance between a point on
the vesicle, $\xx \in \gamma$, and the top half of the confining
geometry. We find all local minimums of $d(\xx,\Gamma_\mathrm{top})$,
with the condition that $d(\xx,\Gamma_\mathrm{top}) < \delta$, where
$\delta$ is a parameter. If no such local minimums exist, then the
vesicle is too far from $\Gamma_\mathrm{top}$ to define a lubrication
layer. If there are two or more local minimums, the left-most, $\xx_L$,
and right-most, $\xx_R$, local minimums form the start and end of the
lubrication layer.  If there is only one local minimum, then $\xx_L$ and
$\xx_R$ are the points on $\gamma$ to the left and right of this local
minimum with the condition that $d(\xx_L,\Gamma_\mathrm{top}) =
d(\xx_R,\Gamma_\mathrm{top}) = \delta$. Then, the segment
$\gamma_{\mathrm{layer}} \subset \gamma$ consists of all points $\xx \in
\gamma$ between $\xx_L$ and $\xx_R$ with the condition that
$d(\xx,\Gamma_\mathrm{top}) < \delta$. Finally, the lubrication layer
width is
\begin{align}
  w_\mathrm{top} = \frac{1}{|\gamma_{_\mathrm{layer}}|} 
    \int_{\gamma_{_\mathrm{layer}}} d(\xx,\Gamma_\mathrm{top}) \, ds.
\end{align}
The region that defines the top and bottom lubrication layers is
illustrated in Figure~\ref{fig:schematic}, and the height of the gray
regions denote the lubrication layer thicknesses. In this example, the
top layer is broken across two different regions.

@@

We start by considering a vesicle with reduced area $\alpha = 0.6$
passing through stenosis with a capillary number $Ca = 0.25$.  With the
current setup and $Ca=0.25$, an elliptical vesicle with reduced area
greater than $\alpha = 0.8$ cannot fit through the closely-fitting
geometry. Figure~\ref{fig:RA6} shows six time steps of a (a) stiff
single-component (b) floppy single-component, and (c) multicomponent
vesicle. The lipid distribution of the multicomponent vesicle is
initially random with a mean value of 0.55. In all plots, the color is
the dimensionless bending modulus of the multicomponent vesicle that
remains bounded in $[0.1,1]$ by using the new sigmoid bending modulus in
Equation~\eqref{eqn:tanhBending}. A single Lagrangian point is included
to visualize any tank-treading behavior. There are slight differences
between the three cases, with the most noticeable being that the
multicomponent vesicle has higher curvature in the floppy region.
However, in general, there is little difference between these cases,
principally because these vesicles have a large reduced area.

@@

We next consider a vesicle with a smaller reduced area $\alpha=0.4$ with
the same geometry and capillary number. Figure~\ref{fig:RA4} shows the
shape of a (a) stiff single-component, (b) floppy single-component, and
(c) multicomponent vesicle at six locations along the stenosis channel.
Contrary to the vesicles with the larger reduced area
(Figure~\ref{fig:RA6}), the bending modulus has a large effect on the
vesicle shape. We first consider the three different energies---bending,
tension, and phase---for each example. In Figure~\ref{fig:Energy}, we
plot these energies as a function of the vesicle's center. 
%As a
%reminder, the vesicle enters the constriction at $x=-15$ and exits at
%$x=15$. 
Note that the single-component vesicles do not have a phase energy. We
observe that, as the vesicle enters the stenosis, it develops regions of
high curvature, and this results in an increase in the bending energy.
As the stiff single-component and multicomponent vesicles reach a
steady-state shape near the middle of the channel, their bending,
tension, and phase energies remain nearly constant from $x=0$ until the
end of the stenosis. For the multiple-component vesicle, this implies
that there is no coarsening of lipid phase parameter in the middle of a
stenosis.

@@

\begin{figure}[h]
  \centering
%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 2cm .5cm},clip]{(a)}{figures/rightSep.pdf}
%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 2cm .5cm},clip]{(b)}{figures/randSep.pdf}
%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 2cm .5cm},clip]{(c)}{figures/leftSep.pdf}
  \includegraphics[width=\columnwidth]{figures/Contracting_RAp6MCp5.pdf}
  \caption{\label{fig:RA6leftRightRand} \small A multicomponent vesicle
  with 50\% floppy region passing through a contracting geometry. The
  vesicle's reduced area is $\alpha = 0.6$ and the capillary number is
  $Ca = 0.25$. The lipid distribution is initialized to be (a) random,
  (b) phase separated with the stiff region leading; (b) random; (c)
  phase separated with the floppy region leading.}
\end{figure}

@@

In addition to the lipid distribution, the percentage of the vesicle
that is floppy plays a role in the vesicle shapes and dynamics.
Therefore, we consider a vesicle with reduced area $\alpha = 0.5$ in the
contracting geometry with various sizes of the floppy region. Motivated
by the last experiment, we initialize the stiff region to be in the
front and the floppy region to be in the back. In each simulation, the
capillary number is $Ca = 0.25$. Figure~\ref{fig:RA5} shows the vesicle
shapes at the same six time steps when the percentage of the floppy
region is (a) 0\% (single-component), (b) 15\%, (c) 25\%, (d) 35\%, and
(e) 45\%. One effect of the size of the floppy region is that the
symmetry of the vesicle shape is broken at smaller percentages. We also
see that stiffer vesicles have faster migration speeds, but the effect
is quite small---Table~\ref{tbl:contractingTimes} reports the time the
vesicle first passes through the neck.
%In Figure~\ref{fig:RA5}, we consider a vesicle with reduced area
%$\alpha = 0.5$ and the capillary number is $Ca = 0.25$. We start with a
%single-component vesicle and then increase the percentage of the
%vesicle membrane that is floppy. By comparing the vesicle location at
%the time step just before the vesicle passes through the constriction,
%we can immediately see that vesicles with membranes that have larger
%percentage of floppy regions reach and pass through the neck earlier.
%The dimensionless times that the entire vesicle first passes through
%the neck are reported in Table~\ref{tbl:contractingTimes}.

>>>>

%%%TITLE, AUTHORS AND ABSTRACT%%%
\twocolumn[
  \begin{@twocolumnfalse}
{\includegraphics[height=30pt]{head_foot/SM}\hfill\raisebox{0pt}[0pt][0pt]{\includegraphics[height=55pt]{head_foot/RSC_LOGO_CMYK}}\\[1ex]
\includegraphics[width=18.5cm]{head_foot/header_bar}}\par
\vspace{1em}
\sffamily
\begin{tabular}{m{4.5cm} p{13.5cm} }
%
\includegraphics{head_foot/DOI} & \noindent\LARGE{\textbf{Hydrodynamics of Multicomponent Vesicles Under Strong Confinement}} \\
\vspace{0.3cm} & \vspace{0.3cm} \\
%
 & \noindent\large{Ashley Gannon,\textit{$^{a}$} Y.-N. Young,\textit{$^{b\ddag}$} and Bryan Quaife\textit{${\ast}${$^{a}$}}} \\
% %Author names go here instead of "Full name", etc.
%
\includegraphics{head_foot/dates} & \noindent\normalsize{%We numerically study the hydrodynamics of multicomponent vesicles in two strongly
  %confining geometries.
  We conduct a numerical investigation into the hydrodynamics of multicomponent vesicles in two strongly confined geometries. This serves as a simplified model for red blood
  cells undergoing large deformations while traversing %when passing through extreme
  narrow constrictions.
  We propose a novel parameterization for the bending modulus that maintains positivity across all lipid phase parameter values.	
  %We propose a new bending modulus parameterization that
  %is positive for all values of the lipid phase parameter. 
  For a multicomponent vesicle passing through a stenosis, %we correlate 
  we establish connections between various properties: lipid phase coarsening, size and flow profile of the lubrication layers, %properties (size and flow profile), 
  excess pressure, and the tank-treading velocity of
  the membrane. For a multicomponent vesicle passing through a
  contracting channel, we find that the lipid always phase separates so
  that the vesicle is stiffer in the front as it passes through the
  constriction. %For both cases of confinement we find that the lipid
  %coarsening is arrested under strong confinement, and proceeds with
  %high rate upon relief from extreme confinement. 
  For both cases of confinement, we find that lipid coarsening is arrested under strong confinement and proceeds at a high rate upon relief from extreme confinement.
  The results may be useful for efficient sorting lipid domains using microfluidic flows by
  controlled release of vesicles passing through strong confinement.} \\
  %The abstrast goes here instead of the text "The abstract should
  %be..."
%
\end{tabular}
%
 \end{@twocolumnfalse} \vspace{0.6cm}
]
%%%END OF TITLE, AUTHORS AND ABSTRACT%%%

@@

%%%MAIN TEXT%%%%
\section{\label{sec:Introduction}Introduction}
Biological membranes, the basic structural units for compartmentalizing
biological systems, %have been observed to contain a vast 
exhibit a diverse array of
proteins and lipid species. %that phase-separate and form
%domains or rafts, resulting in spatial variations in material properties
%such as bending stiffness. 
These lipids undergo phase separation, forming domains or rafts that lead to variations in material properties, including bending stiffness. 
Synthetic multicomponent vesicles,
self-enclosed lipid bilayer membranes composed of different lipid
species, have been used to study the rich patterns and accompanying
morphologies that emerge from elastic heterogeneity in the membrane. In
a quiescent environment, such elastic heterogeneity gives rise to
wrinkling, budding, adhesion, and fusion of vesicle
membranes~\cite{Lowengrub2009_PRE, Li2012_CommMathSci, Zhao2011_PRE},
closely related to several cellular processes~\cite{Rauch2000_BiophysJ,
Takeda2003_PNAS}.
%In a quiescent environment, such elastic heterogeneity gives rise to
%wrinkling budding~\cite{Lowengrub2009_PRE, Li2012_CommMathSci},
%adhesion and fusion~\cite{Zhao2011_PRE} of vesicle membrane, closely
%related to cellular budding and fission
%processes~\cite{Rauch2000_BiophysJ} as well as in cellular adhesion and
%fusion~\cite{Takeda2003_PNAS}.

@@

Under a linear shear flow, a multicomponent vesicle exhibits more exotic
dynamics in both shape and membrane composition than a single-component
vesicle~\cite{soh-tse-li-voi-low2010, Smith2007_JChemPhys,
Cox2015_Nonlinearity, liu-mar-li-vee-low2017, Tusch2018_PRF,
Gera2018_SoftMatter, ger-sal-spa2022}. For example, multicomponent
vesicles under a background flow often exhibit highly complex
morphologies, leading to vesicle budding. The hydrodynamics of these
multicomponent vesicles include phase treading, tumbling with no
viscosity contrast, swinging, budding, and
fission~\cite{soh-tse-li-voi-low2010, wan-du2008, all-ama2006,
ger-sal-spa2022, lip1992, urs-klu-phi2009}. Through numerical
investigations,~\citet{liu-mar-li-vee-low2017} identified several key
dimensionless numbers, including the reduced area, capillary number, and
the floppy-to-stiff ratio to characterize various dynamics of a
two-dimensional multicomponent vesicle in an unbounded linear shear
flow. In addition to the aforementioned numerical studies, these
dynamics have been observed in experiments~\cite{bag-sun2009,
yan-ima-tan2010, yan-ima-tan2008, dre-jah-bob-spa-gop2021}.
%
%Sohn et al. (2010) studied two-dimensional multicomponent vesicles in a
%background shear flow, along with the evolution of distinct surface
%phases, finding highly complex morphologies and dynamics for highly
%deformed vesicles. Smith & Uspal (2007) showed using dissipative
%particle dynamics simulations that a shear flow can be used to separate
%buds from a multicomponent vesicle. The influence of both bending
%rigidity and spontaneous curvature variation on the equilibrium shape
%of a vesicle has also been investigated (Cox & Lowengrub 2015).
%Subsequent boundary integral simulations by Liu et al. (2017) showed a
%transition from tumbling to tank-treading to ‘phase-treading’ of the
%constituents along the surface upon increasing the shear rate. Analytic
%results have also shown that a variation of bending rigidity along a
%surface can induce migration in tank-treading vesicles (Olla 2011).
%Synthetic systems have also been fruitful for testing theoretical
%predictions. Experiments using a two-phase lipid vesicle in such a flow
%as a simplified model of red blood cell dynamics showed similarly
%complex features (Tusch et al. 2018). Gera & Salac (2018b) then used
%simulations to probe a wide array of morphological changes due to
%spatially varying bending stiffness and line tension between two lipid
%phases. The phase separation process itself is naturally of great
%interest, and experiments have been used to study spinodal
%decomposition and viscous fingering along membrane surfaces (Veatch &
%Keller 2003; Lowengrub, Rätz & Voigt 2009; Marenduzzo & Orlandini 2013;
%Stanich et al. 2013).
%
%
%Groups have also studied the behaviors of a vesicle that is composed of
%different types of lipids and proteins. The presence of different lipid
%species has been used to model different processes including the
%bending stiffness, spontaneous curvature, and adhesion
%potential~\cite{zha-das-du2010, tan-yan-ima2011}. The dynamics of these
%multicomponent vesicles include phase treading, tumbling with no
%viscosity contrast, swinging, budding, and
%fission~\cite{soh-tse-li-voi-low2010, wan-du2008, all-ama2006,
%ger-sal-spa2022, lip1992, urs-klu-phi2009}. In addition to the
%aforementioned numerical studies, these dynamics have been observed in
%experiments~\cite{bag-sun2009, yan-ima-tan2010, yan-ima-tan2008,
%dre-jah-bob-spa-gop2021}.
%

@@

The lipid species $u$ is governed by a fourth-order Cahn-Hilliard
equation that results in the lipids phase separating while conserving
their total mass. To model the variable bending,
\citet{soh-tse-li-voi-low2010} parameterized the bending modulus as
\begin{align}
  \label{eqn:linearBending}
  b(u) = (1-u) + \beta u.
\end{align}
However, since the double-well potential does not have hard walls, the
lipid concentration is not guaranteed to be confined to the interval
$[0,1]$. This is problematic since $b(u) < 0$ if $u > (1 - \beta)^{-1}$,
and such values of $u$ are possible when $\beta \ll 1$, $Ca \gg 1$, or
the vesicle is confined to a narrow region. This behavior is
demonstrated in Figure~\ref{fig:concModels}(a) for a vesicle with a
floppy-to-stiff ratio $\beta = 10^{-1}$ entering a stenosis. Using the linear bending model
in Equation~\eqref{eqn:linearBending}, the lipid concentration achieves
a maximum value of $u \approx 1.5$ which results in an instability that
is formed by the resulting unphysical negative bending stiffness. To
rectify this issue, we parameterize the bending modulus with the sigmoid
function
\begin{align}
  b(u) = \frac{\beta-1}{2} \tanh\left(3\left(u-\frac{1}{2} 
    \right)\right) + \frac{\beta + 1}{2}.
  \label{eqn:tanhBending}
\end{align}
This parameterization maps the local minimums of the double-well
potential close to $\beta$ and $1$, but more importantly, b(u) remains
bounded in $(\beta,1)$ even when $u \notin [0,1]$
(Figure~\ref{fig:concModels}(b)). This new bending model is validated in
Section~\ref{sec:validation}.
%To demonstrate the necessity of this new bending model, we consider a
%multicomponent vesicle in strong confinement with both bending
%models~\eqref{eqn:linearBending} and~\eqref{eqn:tanhBending}. The
%stiff-to-floppy ratio is $\beta = 10^{-1}$. In the new
%model~\eqref{eqn:tanhBending}, the lipid concentration achieves a
%maximum value of $u \approx 1.002$ which results in a minimum bending
%stiffness of $b(u) \approx \beta$. However, if we use the linear
%bending model~\eqref{eqn:linearBending}, the lipid concentration
%achieves a maximum value of $u \approx 1.52$ which results in an
%unphysical negative bending stiffness of $b(u) \approx -0.5$. The
%corresponding vesicle shape is in Figure~\ref{fig:concModels}(b), and
%the instability caused by the negative bending stiffness is near the
%region with negative curvature.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Validation}
\label{sec:validation}
We validate the new sigmoid bending model in
Equation~\eqref{eqn:tanhBending} by reproducing dynamics reported in the
literature. Figure~\ref{fig:treading} shows a phase treading (top) and a
tank-treading (bottom) multicomponent vesicle in an unconfined linear
shear flow. The simulations align with the results reported
by~\citet{liu-mar-li-vee-low2017} (cf.~Figure 3 and Figure 4).
\begin{figure}[h]
  \centering
  \includegraphics[width=0.9\columnwidth]{figures/shearTreading.pdf}
%  \subfigimg[width=\columnwidth, trim ={5.5cm 1.5cm 4cm 0},clip]{(a)}{figures/Fig4a.pdf}
%  \subfigimg[width=\columnwidth, trim ={5.5cm 1.5cm 4cm 0},clip]{(b)}{figures/Fig4b.pdf}
  \caption{\label{fig:treading} \small A multicomponent vesicle in a
  linear shear flow undergoes phase-treading (top) and tank-treading
  (bottom) with the new sigmoid bending model in
  Equation~\eqref{eqn:tanhBending}. The dimensionless times are in the
  title. The red region is stiff and the blue region is floppy. The
  simulations qualitatively agree with the results presented
  in~\citet{liu-mar-li-vee-low2017}.}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\label{sec:LL} Lubrication layers and excess pressure}
The lubrication layer between a vesicle and the solid wall plays a
critical role in the dynamics of a vesicle under strong confinement.
Therefore, throughout Section~\ref{sec:results}, we calculate and
analyze the flow inside the lubrication layers between the vesicle and
the channel walls to elucidate the correlation between hydrodynamics and
membrane dynamics. To define the size of the top lubrication layer, we let
$d(\xx,\Gamma_\mathrm{top})$ be the minimum distance between a point on
the vesicle, $\xx \in \gamma$, and the top half of the confining
geometry. The size of the bottom lubrication layer is defined similarly. 
We find all local minimums of $d(\xx,\Gamma_\mathrm{top})$,
with the condition that $d(\xx,\Gamma_\mathrm{top}) < \delta$, where
$\delta$ is a parameter. If no such local minimums exist, then the
vesicle is too far from $\Gamma_\mathrm{top}$ to define a lubrication
layer. If there are two or more local minimums, the left-most, $\xx_L$,
and right-most, $\xx_R$, local minimums form the start and end of the
lubrication layer.  If there is only one local minimum, then $\xx_L$ and
$\xx_R$ are the points on $\gamma$ to the left and right of this local
minimum with the condition that $d(\xx_L,\Gamma_\mathrm{top}) =
d(\xx_R,\Gamma_\mathrm{top}) = \delta$. Then, the segment
$\gamma_{\mathrm{layer}} \subset \gamma$ consists of all points $\xx \in
\gamma$ between $\xx_L$ and $\xx_R$ with the condition that
$d(\xx,\Gamma_\mathrm{top}) < \delta$. Finally, the lubrication layer
width is
\begin{align}
  w_\mathrm{top} = \frac{1}{|\gamma_{_\mathrm{layer}}|} 
    \int_{\gamma_{_\mathrm{layer}}} d(\xx,\Gamma_\mathrm{top}) \, ds.
\end{align}
The region that defines the top and bottom lubrication layers is
illustrated in Figure~\ref{fig:schematic}, and the height of the gray
regions denote the lubrication layer thicknesses. In this example, the
top layer is broken across two different regions.

@@

We start by considering a vesicle with reduced area $\alpha = 0.6$
passing through stenosis with a capillary number $Ca = 0.25$.  With the
current setup and $Ca=0.25$, an elliptical vesicle with reduced area
greater than $\alpha = 0.8$ cannot fit through the closely-fitting
geometry. \color{red} ARG: Is this true for stenosis? I remember it being the 
case for contracting. I'll check previous runs. \color{black} 
Figure~\ref{fig:RA6} shows six time steps of a (a) stiff
single-component (b) floppy single-component, and (c) multicomponent
vesicle. The lipid distribution of the multicomponent vesicle is
initially random with a mean value of 0.55. In all plots, the color is
the dimensionless bending modulus of the multicomponent vesicle that
remains bounded in $[0.1,1]$ by using the new sigmoid bending modulus in
Equation~\eqref{eqn:tanhBending}. A single Lagrangian point is included
to visualize any tank-treading behavior. There are slight differences
between the three cases, with the most noticeable being that the
multicomponent vesicle has higher curvature in the floppy region.
However, in general, there is little difference between these cases,
principally because these vesicles have a large reduced area.

@@

We next consider a vesicle with a smaller reduced area $\alpha=0.4$ with
the same geometry and capillary number. Figure~\ref{fig:RA4} shows the
shape of a (a) stiff single-component, (b) floppy single-component, and
(c) multicomponent vesicle at six locations along the stenosis channel.
Contrary to the vesicles with the larger reduced area
(Figure~\ref{fig:RA6}), the bending modulus has a large effect on the
vesicle shape. We first consider the three different energies---bending,
tension, and phase---for each example. In Figure~\ref{fig:Energy}, we
plot these energies as a function of the vesicle's center. 
%As a
%reminder, the vesicle enters the constriction at $x=-15$ and exits at
%$x=15$. 
Note that the single-component vesicles do not have a phase energy. We
observe that, as the vesicle enters the stenosis, it develops regions of
high curvature, and this results in an increase in the bending energy.
As the stiff single-component and multicomponent vesicles reach a
steady-state shape near the middle of the channel, their bending and
tension energies remain nearly constant from $x=0$ until the
end of the stenosis. For the multicomponent vesicle, the phase energy is 
also nearly constant in this region. This implies
that there is no coarsening of lipid phase parameter in the middle of a
stenosis.

@@

\begin{figure}[h]
  \centering
%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 2cm .5cm},clip]{(a)}{figures/rightSep.pdf}
%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 2cm .5cm},clip]{(b)}{figures/randSep.pdf}
%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 2cm .5cm},clip]{(c)}{figures/leftSep.pdf}
  \includegraphics[width=\columnwidth]{figures/Contracting_RAp6MCp5.pdf}
  \caption{\label{fig:RA6leftRightRand} \small A multicomponent vesicle
  with 50\% floppy region passing through a contracting geometry. The
  vesicle's reduced area is $\alpha = 0.5$ and the capillary number is
  $Ca = 0.25$. The lipid distribution is initialized to be (a) random,
  (b) phase separated with the stiff region leading; (b) random; (c)
  phase separated with the floppy region leading.}
\end{figure}

@@

In addition to the lipid distribution, the percentage of the vesicle
that is floppy plays a role in the vesicle shapes and dynamics.
Therefore, we consider a vesicle with reduced area $\alpha = 0.5$ in the
contracting geometry with various sizes of the floppy region. Motivated
by the last experiment, we initialize the stiff region to be in the
front and the floppy region to be in the back. In each simulation, the
capillary number is $Ca = 0.25$. Figure~\ref{fig:RA5} shows the vesicle
shapes at the same six time steps when the percentage of the floppy
region is (a) 0\% (single-component), (b) 15\%, (c) 25\%, (d) 35\%, and
(e) 45\%. One effect of the size of the floppy region is that the
symmetry of the vesicle shape is broken at smaller percentages. We also
see that stiffer vesicles have faster migration speeds, but the effect
is quite small---Table~\ref{tbl:contractingTimes} reports the time the
vesicle first passes through the neck. \color{red} I think this is backwards? The table reports that the floppiest vesicle made it through the contraction the quickest. \color{black}
%In Figure~\ref{fig:RA5}, we consider a vesicle with reduced area
%$\alpha = 0.5$ and the capillary number is $Ca = 0.25$. We start with a
%single-component vesicle and then increase the percentage of the
%vesicle membrane that is floppy. By comparing the vesicle location at
%the time step just before the vesicle passes through the constriction,
%we can immediately see that vesicles with membranes that have larger
%percentage of floppy regions reach and pass through the neck earlier.
%The dimensionless times that the entire vesicle first passes through
%the neck are reported in Table~\ref{tbl:contractingTimes}.
